---
title: "Lab10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.
Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)

```{r}
library(papaja)
library(dplyr)
library(ggplot2)

all_data <- read.csv("open_data/stroop_data.csv")

(stand_stroop <- t.test(all_data$incongruent_stand,
                         all_data$congruent_stand,
                         paired = TRUE))

(sit_stroop <- t.test(all_data$incongruent_sit,
                         all_data$congruent_sit,
                         paired = TRUE))

stand_stroop_scores <- all_data$incongruent_stand-all_data$incongruent_stand
sit_stroop_scores <- all_data$incongruent_sit-all_data$incongruent_sit

stroop_differences <- sit_stroop_scores - stand_stroop_scores

(paired_results <- t.test(stand_stroop_scores,
                         sit_stroop_scores,
                         paired=TRUE))

(interaction_results <- t.test(stroop_differences))

```
The authors wrote:
The Stroop effects in both the sitting condition, M = 118.9 ms, t(49) = 16.52, p < .01, d = 2.376, and the standing condition, M = 95.9 ms, t(49) = 14.327,p < .01, d = 2.034, were highly reliable
Our reproduction found:
The Stroop effects in both the sitting condition, `r papaja::apa_print(sit_stroop)$full_result`, and the standing condition, `r papaja::apa_print(stand_stroop)$full_result`, were highly reliable

The authors wrote:
but the most significant finding again was the shrinkage of the effect when participants were standing, F(1, 49) = 8.964, p = .004, ηp 2 = .155.
Our reproduction found:
`r apa_print(interaction_results)$full_result`.

Reproduce a graph of the means, like shown in the paper (2 points)
```{r}
library(tidyr)

# convert to long

stroop_df <- all_data %>%
  pivot_longer(cols = 1:4,
              names_to = c("Congruency","Posture"),
              names_sep = "_",
              values_to = "RTs")

# get means

overall_means <- stroop_df %>%
  group_by(Posture,Congruency) %>%
  summarise(meanRT = mean(RTs),
            SEMRT = (sd(RTs)/sqrt(length(RTs))))

# plot

ggplot(overall_means, aes(x=Posture,
                          y=meanRT,
                          group=Congruency,
                          fill=Congruency))+
  geom_bar(stat="identity", position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT-SEMRT),
                postition=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(500,1000))
```

Present a power-curve analysis for the design. (2 points)
```{r}
effect_sizes <- seq(0,1.5,.1)
prop_significant <-c()
for(i in 1:length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value)
  
  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
}
plot_df <- data.frame(effect_sizes,
                      prop_significant)
ggplot(plot_df, aes(x=effect_sizes,y=prop_significant))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks=seq(0,1,.1)) +
  ylab("Proportion Significant")
```

