---
title: "Lab8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.
-Advanced: Have an option so that the function will convert the raw scores to zscores in one of two ways:
-using user provided mean and standard deviation
-using the calculated mean and standard deviation from the raw scores

```{r}

to_zscores <- function(raw,mu,sd){
  zscores <- (raw-mu)/sd
  return(zscores)
}

some_numbers <- c(1,2,3,4,5)

to_zscores(some_numbers,5,1)

# advanced
to_zscores_b <- function(raw,mu=NULL,sd=NULL){
  if(is.null(mu) == TRUE) mu <- mean(raw)
  if(is.null(sd) == TRUE) sdev <- sd(raw)
  zscores <- (raw-mu)/sdev
  return(zscores)
}

to_zscores_b(some_numbers)

```

2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).

-Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).

```{r}

z.test <- function(sample_mean,sample_size,mu,sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail=FALSE)
  return(p_value)

}

z.test(sample_mean = 50,
       sample_size = 25,
       mu = 40,
       sigma = 7)

```

